The language of generalization: Probability, vagueness, and interaction

### 2018-05-14 paper/case1-generics.Rmd
fix legend title in gen endorse fig

```{r generic-endorsement}
load("cached_results/case1_endorseSummary_byItem.RData") # d.gen.endorse.bayes.prev, d.gen.endorse.manipulation.check.bayes
generics.endorsement.spectrum <- ggplot(
    d.gen.endorse.bayes.prev, 
    aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev)
  )+
  geom_bar(stat = 'identity', position = position_dodge(), color='black',  alpha = 1)+
  geom_linerange(position = position_dodge(), size = 1)+
  coord_flip()+
  ylab("Human generic endorsement")+
  xlab("")+
  scale_fill_viridis(breaks = c(0, 1), limits = c(0, 1))+
  scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
  guides(color = guide_colorbar(title = 'Prevalence',
                               ticks = F))+
  theme(legend.position = 'bottom')
```

>>>>

```{r generic-endorsement}
load("cached_results/case1_endorseSummary_byItem.RData") # d.gen.endorse.bayes.prev, d.gen.endorse.manipulation.check.bayes
generics.endorsement.spectrum <- ggplot(
    d.gen.endorse.bayes.prev, 
    aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev)
  )+
  geom_bar(stat = 'identity', position = position_dodge(), color='black',  alpha = 1)+
  geom_linerange(position = position_dodge(), size = 1)+
  coord_flip()+
  ylab("Human generic endorsement")+
  xlab("")+
  scale_fill_viridis(breaks = c(0, 1), limits = c(0, 1))+
  scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
  guides(fill = guide_colorbar(title = 'Referent prevalence',
                               ticks = F))+
  theme(legend.position = 'bottom')
```
